POMDP comparisons across sigma_m, sigma_g

### 2018-01-24 appendix/appendix_harvestfirst.Rmd
overest sims

overest %>% filter(method != "pomdp", sigma_m == "0")  %>%
  bind_rows(
  overest %>% filter(method == "pomdp", sigma_m == "0.15")) %>%
  select(-sigma_m, -sigma_g) %>%
  mutate(method = fct_recode(method,
                             "MSY" = "msy",
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd = 1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  coord_cartesian(ylim = c(0, 1))

>>>>

overest %>% filter(method != "pomdp", sigma_m == "0")  %>%
  bind_rows(
  overest %>% filter(method == "pomdp", sigma_m == "0.15")) %>%
  select(-sigma_m, -sigma_g) %>%
  mutate(method = fct_recode(method,
                             "MSY" = "msy",
                             "CE" = "det",
                             "TAC" = "pgy",
                             "POMDP" = "pomdp")) %>%
  write_csv(file.path(log_dir, "overest_sims.csv"))
```

```{r}
read_csv(file.path(log_dir, "overest_sims.csv")) %>%
  ggplot(aes(time, mean, col=method, fill=method)) + 
  geom_line(lwd = 1) + 
  geom_ribbon(aes(ymax = mean + sd, ymin = mean-sd), col = NA, alpha = 0.1) +
  coord_cartesian(ylim = c(0, 1))
